%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\usepackage{zh_CN-Adobefonts_external} 
\usepackage{linespacing_fix}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape  Heng Guo} \\ \vspace{4pt}
    \small 070-1322-8279 $|$ \href{mailto:heng.guo@ist.osaka-u.ac.jp}{\underline{heng.guo@ist.osaka-u.ac.jp}} $|$ 
    \href{https://gh-home.github.io/}{\underline{Homepage}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Electronic Science and Technology of China (UESTC) }{Chengdu, China}
      {Bachelor of Electronic Engineer}{Aug. 2015 -- Sep. 2011}
  \resumeSubheading
      {University of Electronic Science and Technology of China (UESTC)}{Chengdu, China}
      {Master of Signal Processing}{Aug. 2018 -- Sep. 2015}
   \resumeSubheading
 		{Osaka University}{Osaka, Japan}
 		{Doctor of Computer Science}{Present -- Sep. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant}{Oct. 2018 -- Present}
      {Osaka University}{Osaka, Japan}
      
% -----------Multiple Positions Heading-----------
    \resumeSubheading
     {Research Intern}{June 2016 -- Jan. 2017}
	{AI lab of Qihoo 360 Technology Co. Ltd.}{Beijing, China}
     \resumeItemListStart
		\resumeItem{Propose a real-time video stabilization algorithm for user-captured videos with 0.5s delay.}
		\resumeItem{Implement an android application for real-time video stabilization.}
     \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Honors}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Excellent Master Thesis of UESTC (Top 3\%)}{June 2018}
   
         \resumeProjectHeading
   {Excellent Postgraduate of UESTC (Top 6\%))}{June 2018}
         \resumeProjectHeading
   {National Scholarship of China(Top 2\%))}{Oct. 2017}
         \resumeProjectHeading
   {Academic Scholarship of UESTC (Top 10\%)}{2015 \& 2016 \& 2017}
         \resumeProjectHeading
   {Excellent Graduate of UESTC (Top 7\%)}{Sep. 2015}
         \resumeProjectHeading
   {The 1st Prize of National College Student Information Security Contest}{July 2014}
            \resumeProjectHeading
   {The 2nd Prize of National Undergraduate Electronics Design Contest}{Sep. 2013}
   \resumeProjectHeading
   {People's Scholarship (Top 15\%)}{2011 \& 2012 \& 2013}
   \resumeProjectHeading
   {Outstanding Individual in Social Practice}{Sep. 2012}
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Publication}
%\renewcommand\labelenumi{(\theenumi)}
\begin{enumerate}[label={[\arabic*]}]
	\item Guo Heng, et al. ``Multispectral Photometric Stereo for Spatially-Varying Spectral Reflectances: A well posed problem?" IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2021}). 
	\item Guo Heng, et al. ``Self-calibrating Near-light Photometric Stereo under Anisotropic Light Emission." Meeting on Image Recognition and Understanding (\textbf{MIRU 2020 Best student paper}).  
	\item Guo Heng, et al. ``Joint video stitching and stabilization from moving cameras." IEEE Transactions on Image Processing (\textbf{TIP 2016}).
	\item Guo Heng, et al. ``View-consistent meshflow for stereoscopic video stabilization." IEEE Transactions on Computational Imaging (\textbf{TCI 2018}).
	\item Guo Heng, et al. ``Joint bundled camera paths for stereoscopic video stabilization." IEEE International Conference on Image Processing (\textbf{ICIP 2016 Oral}).
	\item Guo Heng, et al. ``Multispectral Photometric Stereo for Spatially-Varying Spectral Reflectances" International Journal of Computer Vision. (IJCV under review). 
	\item Guo Heng, et al. ``Patch-based uncalibrated photometric stereo under natural illumination" 
	IEEE Transactions on Pattern Analysis and Machine Intelligence. (TPAMI under review). 
\end{enumerate}

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Program language}{: Java, Python, C/C++} \\
     \textbf{Certificacts}{: TOEFL (95), CET-6 (527)} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
