
\begin{enumerate}[label={[\arabic*]}]
	\item Wenjie Li, Jinglei Shi, Jin Han, \textbf{Heng Guo}$^\dagger$, Zhanyu Ma. ``Seeing Through the Rain: Resolving High-Frequency Conflicts in Deraining and Super-Resolution via Diffusion Guidance.'' AAAI Conference on Artificial Intelligence. (\textbf{AAAI 2025}).
	\item Zhenyu Jin, Wenjie Li, Zhanyu Ma, \textbf{Heng Guo}$^\dagger$. ``SpecGen: Neural Spectral BRDF Generation via Spectral-Spatial Tri-plane Aggregation.'' IEEE Winter Conference on Applications of Computer Vision. (\textbf{WACV 2026}).
	\item Wenjie Li, Xiangyi Wang, \textbf{Heng Guo}$^\dagger$, Guangwei Gao, Zhanyu Ma. ``Self-Supervised Selective-Guided Diffusion Model for Old-Photo Face Restoration.'' Annual Conference on Neural Information Processing Systems. (\textbf{NeurIPS 2025}).
	\item Wenjie Li, \textbf{Heng Guo}$^\dagger$, Yuefeng Hou, Guangwei Gao, Zhanyu Ma. ``Dual-domain Modulation Network for Lightweight Image Super-Resolution.'' IEEE Transactions on Multimedia. (\textbf{TMM 2025}).
	\item Yufei Han, Bowen Tie, \textbf{Heng Guo}$^\dagger$, Youwei Lyu, Si Li$^\dagger$, Boxin Shi, Yunpeng Jia, Zhanyu Ma. ``PolGS: Polarimetric Gaussian Splatting for Fast Reflective Surface Reconstruction.'' IEEE International Conference on Computer Vision. (\textbf{ICCV 2025}).
	\item Kailong Zhang, Youwei Lyu, \textbf{Heng Guo}$^\dagger$, Si Li, Zhanyu Ma, Boxin Shi. ``PolarAnything: Diffusion-based Polarimetric Image Synthesis.'' IEEE International Conference on Computer Vision. (\textbf{ICCV 2025 \color{red}{Highlight}}).
	\item Chu Zhou, Yixin Yang, Junda Liao, \textbf{Heng Guo}, Boxin Shi, Imari Sato. ``Polarimetric Neural Field with Unified Complex-Valued Wavefunction.'' IEEE International Conference on Computer Vision. (\textbf{ICCV 2025}).
	\item Mingzhi Pei, Xu Cao, Xiangyi Wang, \textbf{Heng Guo}$^\dagger$, Zhanyu Ma. ``PMNI: Pose-free Multi-view Normal Integration for Reflective and Textureless Surface Reconstruction.'' IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2025}).
	\item Shuangfan Zhou, Chu Zhou, Youwei Lyu, \textbf{Heng Guo}$^\dagger$, Zhanyu Ma, Boxin Shi, Imari Sato. ``PIDSR: Complementary Polarized Image Demosaicing and Super-Resolution.'' IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2025}).
	\item Mengqiu Xu, Kaixin Chen, \textbf{Heng Guo}, Yixiang Huang, Ming Wu, Zhenwei Shi, Chuang Zhang, Jun Guo. ``MFogHub: Bridging Multi-Regional and Multi-Satellite Data for Global Marine Fog Detection and Forecasting.'' IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2025}).
	\item Songyun Yang, Yufei Han, Jilong Zhang, Kongming Liang, Peng Yu, Zhaowei Qu, \textbf{Heng Guo}. ``RotatedMVPS: Multi-view Photometric Stereo with Rotated Natural Light.'' IEEE Conference on Multimedia and Expo. (\textbf{ICME 2025 \color{red}Oral}).
	\item Youwei Lyu$^*$, \textbf{Heng Guo}$^*$, Kailong Zhang, Si Li, Boxin Shi. ``SfPUEL: Shape from Polarization under Unknown Environment.'' Annual Conference on Neural Information Processing Systems. (\textbf{NeurIPS 2024}).
	\item Li Wenjie, \textbf{Heng Guo}$^\dagger$, Xuannan Liu, Kongming Liang, Jiani Hu, Zhanyu Ma, Jun Guo. ``Efficient Face Super-Resolution via Wavelet-Based Feature Enhancement Network.'' ACM International Conference on Multimedia. (\textbf{ACM MM 2024}).
	\item \textbf{Heng Guo}$^*$, Jieji Ren$^*$, Feishi Wang$^*$, Boxin Shi, Mingjun Ren, Yasuyuki Matsushita. ``DiLiGenRT: A Photometric Stereo Dataset with Quantified Roughness and Translucency.'' IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2024}).
	\item Yufei Han, \textbf{Heng Guo$^\dagger$}, Koki Fukai, Hiroaki Santo, Boxin Shi, Fumio Okura, Zhanyu Ma, Yunpeng Jia. ``NeRSP: Neural 3D Reconstruction for Reflective Objects with Sparse Polarized Images.'' IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2024}).
	\item Feishi Wang$^*$, Jieji Ren$^*$, \textbf{Heng Guo}$^*$, Mingjun Ren, Boxin Shi. ``DiLiGenT-Pi: Photometric Stereo for Planar Surfaces with Rich Details – Benchmark Dataset and Beyond.'' International Conference on Computer Vision. (\textbf{ICCV 2023}).
	\item Jun Hoong Chan, Bohan Yu, \textbf{Heng Guo}, Jieji Ren, Zongqing Lu, Boxin Shi. ``ReLeaPS: Reinforcement Learning-based Illumination Planning for Generalized Photometric Stereo.'' International Conference on Computer Vision. (\textbf{ICCV 2023}).
	\item Jipeng Lv, \textbf{Heng Guo$^{\dagger}$}, Guanying Chen, Jinxiu Liang, Boxin Shi. ``Non-Lambertian Multispectral Photometric Stereo via Spectral Reflectance Decomposition.'' International Joint Conferences on Artificial Intelligence (\textbf{IJCAI 2023}).
	\item \textbf{Heng Guo}, Boxin Shi, Yasuyuki Matsushita. ``Neural BRDF Plugin for Unsupervised Photometric Stereo.'' IEEE International Conference on Network Intelligence and Digital Content (\textbf{IC-NIDC 2023 best paper}).
	\item Feiran Li$^*$, \textbf{Heng Guo}$^*$, Hiroaki Santo, Fumio Okura, Yasuyuki Matsushita. ``Learning to Synthesize Photorealistic Dual-pixel Images from RGBD frames.'' International Conference on Computational Photography (\textbf{ICCP 2023}).
	\item Lilika Makabe, \textbf{Heng Guo}, Hiroaki Santo, Fumio Okura, Yasuyuki Matsushita. ``Near-light Photometric Stereo with Symmetric Lights.'' International Conference on Computational Photography. (\textbf{ICCP 2023}).
	\item \textbf{Heng Guo}, Fumio Okura, Boxin Shi, Takuya Funatomi, Yasuhiro Mukaigawa, Yasuyuki Matsushita. ``Multispectral Photometric Stereo for Spatially-Varying Spectral Reflectances.'' International Journal of Computer Vision. (\textbf{IJCV 2022}). 
	\item \textbf{Heng Guo$^*$}, Zhipeng Mo$^*$, Boxin Shi, Feng Lu, Sai-Kit Yeung, Ping Tan, Yasuyuki Matsushita. ``Patch-based Uncalibrated Photometric Stereo under Natural Illumination.'' 
	IEEE Transactions on Pattern Analysis and Machine Intelligence. (\textbf{TPAMI 2021}). 
	\item \textbf{Heng Guo}, Fumio Okura, Boxin Shi, Takuya Funatomi, Yasuhiro Mukaigawa, Yasuyuki Matsushita. ``Multispectral Photometric Stereo for Spatially-Varying Spectral Reflectances: A Well-posed Problem?'' IEEE Conference on Computer Vision and Pattern Recognition. (\textbf{CVPR 2021}). 
	\item \textbf{Heng Guo}, Boxin Shi, Michael Waechter, Yasuyuki Matsushita. ``Self-calibrating Near-light Photometric Stereo under Anisotropic Light Emission.'' Meeting on Image Recognition and Understanding (\textbf{MIRU 2020 outstanding paper}).  
	\item \textbf{Heng Guo}, Shuaicheng Liu, Shuyuan Zhu, Heng Tao Shen, Bing Zeng. ``View-Consistent MeshFlow for Stereoscopic Video Stabilization.'' IEEE Transactions on Computational Imaging. (\textbf{TCI 2018}).
	\item \textbf{Heng Guo}, Shuaicheng Liu, Tong He, Shuyuan Zhu, Bing Zeng, Moncef Gabbouj. ``Joint Video Stitching and Stabilization from Moving Cameras.'' IEEE Transactions on Image Processing (\textbf{TIP 2016}).
	\item \textbf{Heng Guo}, Shuaicheng Liu, Shuyuan Zhu, Bing Zeng. ``Joint Bundled Camera Paths for Stereoscopic Video Stabilization.'' International Conference on Image Processing. (\textbf{ICIP 2016}) (Oral).
\end{enumerate}